---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# politicsR

<!-- badges: start -->
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/politicsR)](https://cran.r-project.org/package=politicsR)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/3xp80q2vnwfxwhif/branch/main?svg=true)](https://ci.appveyor.com/project/silvadenisson/politicsr/branch/main)
[![DOI](https://zenodo.org/badge/57716660.svg)](https://zenodo.org/badge/latestdoi/7716660)

<!-- badges: end -->

`politicsR` is an R package designed to help political science researchers in calculating conventional party system and political metrics. It offers a comprehensive set of functions for calculating a wide range of indicators, including:

- Party System Fractionalization Index as proposed by Douglas Rae ([1968](https://journals.sagepub.com/doi/abs/10.1177/001041406800100305?journalCode=cpsa))

- Effective Number of Political Parties by Laakso, M., & Taagepera, R. ([1979](https://journals.sagepub.com/doi/abs/10.1177/001041407901200101?journalCode=cpsa))

- Party Nationalization Index by Jones, M. P., & Mainwaring, S. ([2003](https://journals.sagepub.com/doi/abs/10.1177/13540688030092002?journalCode=ppqa))

- Rice Party Cohesion Index by Rice ([1925](https://www.jstor.org/stable/2142407)); and many more.


## Installation

You can install the development version of `politicsR` from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("silvadenisson/politicsR")
```

## Basic usage

To get started with `politicsR`, load the package with:

```{r}
library(politicsR)
```

Then you can start calculating diffent metrics, such as the Herfindahl-Hirschman Concentration Index (HH):

```{r}
x <- c(0.1, 0.1, 0.3, 0.5)
hh(x)
```

Or the Effective Number of Political Parties (ENP):


```{r}
enp(x)
```

The `politicsR` package also contains a few datasets with electoral results that can be used to test its functions. These datasets are organized by the [Constituency-Level Elections Archive (CLEA)](https://electiondataarchive.org/) project and provide a rich source of information for political analysis. With these datasets and the functions provided by the package, users can easily calculate political science metrics such as Douglas Rae’s Fractionalization Index:


```{r}
data(spain)
barc2019 <- spain[spain$yr == 2019 & spain$cst_n == "Barcelona",]
fractionalization(barc2019$pvs1)
```











