---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# politicsR

<!-- badges: start -->
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/politicsR)](https://cran.r-project.org/package=politicsR)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/3xp80q2vnwfxwhif/branch/main?svg=true)](https://ci.appveyor.com/project/silvadenisson/politicsr/branch/main)
<!-- badges: end -->

`politicsR` is an R package designed to help political science researchers in calculating conventional political metrics. It offers a comprehensive set of functions for calculating a wide range of political system indicators, including:

- Party System Fractionalization Index as proposed by Douglas Rae ([1968](https://journals.sagepub.com/doi/abs/10.1177/001041406800100305?journalCode=cpsa))

- electoral system efficiency, party system fragmentation, parliamentary voting patterns; and more.


## Installation

You can install the development version of `politicsR` from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("silvadenisson/politicsR")
```

## Basic usage

To get started with `politicsR`, load the package with:

```{r}
library(politicsR)
```

Then you can start calculating diffent metrics, such as the Herfindahl-Hirschman Concentration Index (HH):

```{r}
x <- c(0.1, 0.1, 0.3, 0.5)
hh(x)
```

Or the Effective Number of Political Parties (ENP):


```{r}
enp(x)
```















