---
title: "Calculating Political System Metrics with `politicsR`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Calculating Political System Metrics with `politicsR`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction

This vignette provides an introduction to `politicsR`. The package offers a variety of basic indicators related to electoral systems, party systems, elections, and parliamentary studies such as the Volatility Index by Perdersen (1979); the Herfindahl–Hirschman concentration index; and the Effective Political Parties proposed by Laakso and Taagepera (1979).

# Installation

You can install the package from CRAN with:

```{r, eval=FALSE}
install.packages("politicsR")
```


Or you can install the development version from [GitHub](https://github.com/silvadenisson/politicsR) to use new features and bug fixes with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("silvadenisson/politicsR")
```

With the package properly installed, we'll load it to use its functions and data in the rest of this vignette:

```{r}
library(politicsR)
```

To test the package's main functionality, we can use the three built-in datasets with electoral results by district in Brazil, Spain or Denmark. To load these data, simply use:

```{r}
data(denmark)
data(brazil)
data(spain)
```

# Usage

## Example 1: Concentration and fragmentation

## Example 2: Party system volatility

## Example 3: Disproportionality between votes and seats

## Example 4: Party system nationalization















